Predator-prey interactions remain stable across a predator's experience in an online videogame

### 2023-06-07 manuscript/Chapter2-manuscript.Rmd
updated discussion

---
title: "Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: ecology.csl
---

@@

\newpage
# ABSTRACT {.unnumbered}

@@

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017]. This is reflected in the literature showing contrasting results in the links between specialization and fitness at the individual level. Some studies have found greater success for individuals that use specialized foraging tactics [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021]. This disrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility. However, many studies have found that both type of foragers can also attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018]. It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010]. While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how? Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011]. Thus, uncovering the role of learning during direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.

@@

In this study, we evaluated how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*. First, we investigate how predators develop their individual hunting expertise. We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued. For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often. Second, we test the hypothesis that experience will shape individual foraging specialization. We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e. IIV) in movement speed across matches, where low IIV translates to individual specialization (e.g. always using a fast tactic). If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds. If experience increases a tactic's efficiency for specific types of prey assuming that all individuals encounter similar groups of prey, then they may instead specialize in their speed. In both scenarios, among individual variation in IIV (i.e. individual differences in specialization) should be low across experience because everyone is either a flexible or a specialist forager, but the population variance would either increase (flexibility) or decrease (specialization). Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV should increase. In this case, we expect predators that experienced more predictable encounters with their prey (i.e. similar groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e. heterogeneous groups across matches) should adopt flexible movement speeds. If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.

@@

We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a]. We fitted the model on both the predator ($Y_{1}$) and prey ($Y_{2}$) speeds using a Gaussian error distribution, and on the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.

The model simultaneously estimated three distinct individual components for each trait across experience levels. The first component, estimated on the mean part of the model, is among individual variation in mean speed and success. This allows to test for individual differences in tactic use (i.e. along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption. The second component, estimated on the dispersion part of the model by modeling the residuals, is among individual variation in intra-individual variation (IIV). This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization. A general intercept is also fitted on both the mean and dispersion part of the model, providing population-level estimates of the aforementioned parameters. The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience. This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.

For the predator and the prey speed, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model. We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model. The dispersion part included individual predator identity random effects exclusively. For hunting success, we modeled the mean part only and controlled for the standardized prey rank and game duration, and included an individual identity random effect.

@@

The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1). Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1). At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2). However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in IIV from novice to advanced (Figure 2). `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e. >0.2 change in standard deviation; Figure 3). In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` almost no change with experience (i.e. <0.05 change in standard deviation).

@@

Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, and movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009]. However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022]. Our results show that predators in *DBD* increased their hunting success with experience substantially, suggesting that learning through repeated interactions played a role in the development of predator expertise. While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, we found that individual predators developed their own behavioural trajectories over successive encounters with the prey. This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience. The behavioural strategies of predators and prey were matched across experience, as both were probably adjusting to each other with specialized cursorial hunters encountering similar groups of prey while slower and flexible hunters encountered varying groups of prey. Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.

@@

The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019]. The prey's speed was important in mediating this pattern as well as the differences in expertise acquisition found among individual predators. Our results suggest that this was in due to the prey increasing their speed as predators gained experience, which may have made hunting more difficult for less skilled hunters. In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022]. Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey are more difficult to capture. Thus, predators that ellicited faster speeds on their prey probably struggled more to develop their expertise if they couldn't properly hunt at high speeds.

However, even after we took prey speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved. For example, the prey could use camouflage or hiding to avoid detection by the predator [Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011]. This could result in predators varying in their expertise if they do not learn equally how to exploit the visual cues that facilitate cryptic prey detection such as habitat characteristics [@Ehlinger1989;@Hughes.etal1992;@Warburton2003] or prey colour patterns [@Szopa-Comley.etal2020]. Another important component of predator expertise and learning is the time delay between hunting events. In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape pattern anticipation than one that played 300 matches in the span of 6 days. While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022]. There are thus interesting avenues for research on the relationship between learning, forgetting, and skill acquisition throughout an individual's experience to better understand predator foraging and predict its consequences.

## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
*je suis rendu ici*
There were only weak differences among predators in tactic use (i.e. mean speed), but differences in specialization were important and related to how different were the groups of prey that they encountered. Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy. Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022]. However, it remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008]. Here, we found that all hunters along the flexible-specialist continuum achieved similar success throughout the study period (Appendix S1: Figure S2). Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.

Surprisingly, the effect of experience on foraging behaviour was much more subtle than we expected. For instance, the predator population maintained their speed and degree of specialization throughout the study period, and individual differences in mean speed did not change with experience. However, differences among predators in foraging specialization did increase slightly with experience, with some individuals becoming increasingly flexible. Interestingly, the behavioural response (i.e. specialization) to experience by individual predators differed. For instance, 44% of the population did not alter their degree of specialization with experience (i.e. remaining either faster and more specialized, or slower and more flexible), while 56% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience. These changes were accompanied by predators increasingly matching their specialization to the mean speed of the prey groups across experience, instead of the variability between encounters. This suggests that it may be easier for predators to specialize on their prey by relying on mean cues (i.e. mean behaviour) instead of relying solely on resource heterogeneity [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].

*expliquer pourquoi les généralistes ont moins bien performé ici*

It is likely that predators were also driving changes in prey behaviour because most predator-prey behavioural relationships remained stable even though half of the population switched from a specialist to a flexible strategy and vice-versa across experience. This implies that the prey were probably also learning how to avoid predation through repeated interactions. Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success. These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], but their broader consequences remain unclear. Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].

While experience did not alter most of the interaction, predators still managed to increase foraging specialization with increasing prey speed across experience, while individual differences in hunting success simultaneously decreased. When prey express defensive phenotypes such as high speeds, selection on predators should be strong because of the consequences of repeated failures. If predators improve their exploitative ability, then the consequences of hunting these prey should decrease [@BrodieIII.BrodieJr.1999]. Similarly, theoretical studies predict that learning may attenuate selection [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007], but failing to account for reciprocal interactions may mask more complex outcomes. Here, learning appears to have reduced differences in success among predators, but success remained lower when predators hunted faster prey. Again, if prey learned how to avoid the predators, then this would explain why advanced hunters still struggled to achieve similar success against faster prey compared to slower prey. Thus, disentanling the consequences of learning from reciprocal interactions may reveal important insights on predator-prey interactions.

@@

Trait-mediated interactions that affect prey capture are the most important processes driving predator-prey dynamics [@abramsEvolutionPredatorPreyInteractions2000]. While most studies assume that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild. By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise. With experience, the population became increasingly distinct along a flexible-specialist continuum, while interactions remained largely stable. Overall, all hunters achieved similar hunting success. Our results have potential applications for predator-prey models of trait-matching. For instance, simulation studies could incorporate individual variation in experience or learning to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility. Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021]. We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

>>>>

---
title: "Predator-prey interactions remain stable across a predator's experience in an online videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: ecology.csl
---

@@

# ABSTRACT {.unnumbered}

@@

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017]. Some studies have found greater success for individuals specializing on a foraging tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021]. This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility. However, many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018]. It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010]. While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how. Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011]. Uncovering the role of experience in shaping direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.

@@

In this study, we evaluated how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*. First, we investigate how predators develop their individual hunting expertise. We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued. For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often. Second, we test the hypothesis that experience will shape individual foraging specialization. We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e. IIV) in movement speed across matches, where low IIV translates to individual specialization (e.g. always using a fast tactic). If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds. However, if individuals encounter similar groups of prey, then the efficiency of a specific tactic should increase with experience and everyone should instead specialize in their speed. In both scenarios, among individual variation in IIV (i.e. individual differences in specialization) would be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization). Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV would increase. In this case, we expect predators that experienced more predictable encounters with their prey (i.e. similar groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e. heterogeneous groups across matches) should adopt flexible movement speeds. If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.

@@

We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a]. For each experience level, we fitted the model on three traits: the predator's speed ($Y_{1}$) and the prey's speed ($Y_{2}$) using a Gaussian error distribution, and the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution. Fixed and random effect structure were trait-specific and the same for all experience levels. The predator and the prey speed included a mean and a dispersion part. For both traits, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model. We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model. The dispersion part included individual predator identity random effects exclusively. For hunting success, we modeled the mean part only and controlled for the standardized prey rank and game duration, and included an individual identity random effect.

The model simultaneously estimated three individual components for each trait across experience levels. The first component, estimated on the mean part of the model, is among individual variation in mean speed and success. This allows to test for individual differences in tactic use (i.e. along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption. The second component, estimated on the dispersion part of the model by modeling the residuals, is among individual variation in intra-individual variation (IIV). This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization. A general intercept is also fitted on both the mean and dispersion part of the model, providing population-level estimates of the aforementioned parameters. The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience. This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.

@@

The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1). Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1). At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2). However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 2). `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e. >0.2 change in standard deviation; Figure 3). In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e. <0.05 change in standard deviation).

@@

Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, and movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009]. However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022]. We found that predators in *DBD* increased their hunting success with experience substantially, suggesting that learning through repeated interactions played a role in the development of predator expertise. While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey. This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience. The behavioural strategies of predators and prey were matched across experience, as both were probably adjusting to each other with specialized cursorial hunters encountering similar groups of prey while slower and flexible hunters encountered varying groups of prey. Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.

@@

Our results suggest that expertise is honed through extensive practice, but also depends on an individual's capacity to adjust to difficulty. The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019]. The prey's speed was important in mediating this pattern as well as the observed differences in expertise acquisition among predators, probably because the prey increased their speed as predators gained experience. We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022]. Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why they are more difficult to capture. Thus, predators that couldn't properly hunt at high speeds or develop counterstrategies for faster prey were at a disadvantage.

However, even after we took prey speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved. For example, if the prey used camouflage or hiding to avoid being detected by the predator [Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011], then predators may only find them if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@Ehlinger1989;@Hughes.etal1992;@Warburton2003;@Szopa-Comley.etal2020]. In addition, longer time delays between hunting events may exacerbate slower learning or even forgetting [@Endler1991;@Wright.etal2022]. In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.

The predator population maintained their speed and degree of specialization throughout the study period, and all individuals used a similar tactic (i.e. mean speed). However, differences in specialization were important and increased slightly with experience. Predators that specialized in hunting at high speeds encountered groups of prey with similar speeds across matches, while those that adopted a slower and flexible strategy encountered varying groups of prey. This pattern might arise because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Szopa-Comley.Ioannou2022]. However, it is more plausible that this reflects reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], because prey can also learn how to avoid predation [REFS].

Surprisingly, although predators changed their specialization across experience, the behavioural interactions between the predator and the prey remained generally stable. This may in part be due to almost half (44%) of the population showing close to no change in specialization with experience. If these predators were already successful as novices, then there would be no point to change their tactic with experience. However, 66% of the predator population did alter their behaviour with experience to different degrees. Thus, if the prey also learned through repeated interactions with the predators, then it is possible that it also contributed in stabilizing the system, similar to Red Queen dynamics [@brockhurst2014].

The coupling of blabla...pour commencer le paragraphe (moins mettre l'accent sur le changement mais sur le type de relation et ce qui la drive)

When predators were novices, our results align with a matching-response relationship [@Mougi.Kishida2009], because faster-specialist and slower-flexible hunters preyed upon different prey, but they both overall achieved similar success. As predators became advanced, slower-flexible hunters became marginally less successfull, suggesting that faster-specialist hunters were probably learning better how to hunt since faster prey were also more difficult to capture. *ici ajouter que le long term de ça n'est pas certain. il faut que je lise de la littérature explicant pourquoi ça peut être moins bon d'être généraliste*

These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], but their broader consequences remain unclear.

flexible hunters were slightly less successful than specialists. *expliquer pourquoi les généralistes ont moins bien performé ici*
*Modifier cette phrase pour appuyer que les généralistes étaient moins bons à long terme: It remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008].*

*Moreover, even though the relationship was weak, there was an important change in the correlation between the predator's IIV and the mean speed of the prey they encountered.* *pas sûr que je vais ajouter ça*

*ici c'est mon bout sur le matching response je crois...*
When prey express defensive phenotypes such as high speeds, selection on predators should be strong because of the consequences of repeated failures. If predators improve their exploitative ability, then the consequences of hunting these prey should decrease [@BrodieIII.BrodieJr.1999]. Similarly, theoretical studies predict that learning may attenuate selection [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007], but failing to account for reciprocal interactions may mask more complex outcomes. Here, learning appears to have reduced differences in success among predators, but success remained lower when predators hunted faster prey. Again, if prey learned how to avoid the predators, then this would explain why advanced hunters still struggled to achieve similar success against faster prey compared to slower prey. Thus, disentanling the consequences of learning from reciprocal interactions may reveal important insights on predator-prey interactions.

@@

A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild. By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found *support of our prediction that...*

*Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.*

that individual predators displayed large differences in the development of their expertise. With experience, the population became increasingly distinct along a flexible-specialist continuum, while interactions remained largely stable. Overall, all hunters achieved similar hunting success.

Virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021]. We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
